Real Time Fluid Simulation \\ \smaller using Smoothed-Particle Hydrodynamics and OpenGL

### 2014-12-14 paper/paper.tex
Added some SPH stuff to article

\usepackage{listings}

@@

\section{The Algorithm}
%
In the following, we denote the position for the particle $i$ at time $t$ as $x_i^t$, its velocity as $v_i^t$ and its acceleration as $a_i^t$.
We omit the vector notation ($\boldsymbol{x},\boldsymbol{v},\boldsymbol{a}$) for these quantities, since the following equations are valid for the vectors as well as for each component individually.
\par\medskip
%
As suggested in \cite{generalizedwallboundary}, we use the \emph{Velocity-Verlet} time stepping scheme as follows:
%
\begin{algorithm}
	\caption{Single Timestep with Velocity Verlet Algorithm}
	\KwData{$x_i^t$, $v_i^{t - \frac{\Delta t}{2}}$, $a_i^t$, $\Delta t$}
	\KwResult{$x_i^{t + \Delta t}$, $v_i^{t + \frac{\Delta t}{2}}$, $a_i^{t + \Delta t}$}	
	$v_i^{t+\frac{\Delta t}{2}} = v_i^{t - \frac{\Delta t}{2}} + \Delta t a_i^t$ \;
	$x_i^{t+\Delta t} = x_i^t + \Delta t v_i^{t+\frac{\Delta t}{2}}$ \;	
	$a_i^{t + \Delta t} = a_i^{t + \Delta t} (x_i^{t + \Delta t}, m_i)$ from equation \ref{math:acceleration} \;
\end{algorithm}

@@

>>>>

\usepackage{listings}
\usepackage{placeins}

@@

\section{The Algorithm}
%
In the following, we denote the position for the particle $i$ at time $t$ as $x_i^t$, its velocity as $v_i^t$ and its acceleration as $a_i^t$.
We omit the vector notation ($\boldsymbol{x},\boldsymbol{v},\boldsymbol{a}$) for these quantities, since the following equations are valid for the vectors as well as for each component individually.
\par\medskip
%

@@

Several resources point out the algorithms to be used for applying SPH to Fluid Dynamics, the algorithm is described particularly clearly in \cite{kennyerleben} and can be summarized as follows:
%
\FloatBarrier
\begin{algorithm}
	\caption{SPH simulation}
	\For{$i = 1, \dots, N_{\text{Particles}}$}{
		Compute the density of the $i$th particle
		\begin{align*}
			\rho_i = \sum_j m_j W(\| x_i - x_j \|, h)
		\end{align*}
		Compute the pressure of the $i$th particle
		\begin{align*}
			p_i = k (\rho_i - \rho_0)
		\end{align*}
		Compute the interaction forces acting on the $i$th particle, consisting of pressure forces, viscosity and gravity
		\begin{align*}
			f_i^p &= - \sum_j m_j \frac{p_i + p_j}{2 \rho_j} \nabla W(\| x_i - x_j \|, h) \\
			f_i^v &= \mu \sum_j m_j \frac{v_j + v_i}{\rho_j} \nabla^2 W(\| x_i - x_j \|, h) \\
			f_i^{\text{total}} &= f_i^p + f_i^v + g
		\end{align*}
		Solve the differential equation
		\begin{align}
			\begin{aligned}
				\dot{x}_i &= v_i \\
				\dot{v}_i &= \frac{f_i}{\rho_i}
			\end{aligned}
			\label{math:ode}
		\end{align}
	}
\end{algorithm}
\FloatBarrier
%
In our implementation, we use the Velocity Verlet (or Leap-Frog) scheme to solve the ODE \ref{math:ode}, as suggested in \cite{generalizedwallboundary}.
The scheme looks as follows:
%
\begin{algorithm}
	\caption{Single Timestep with Velocity Verlet Algorithm}
	\KwData{$x_i^t$, $v_i^{t - \frac{\Delta t}{2}}$, $a_i^t$, $\Delta t$}
	\KwResult{$x_i^{t + \Delta t}$, $v_i^{t + \frac{\Delta t}{2}}$, $a_i^{t + \Delta t}$}	
	$v_i^{t+\frac{\Delta t}{2}} = v_i^{t - \frac{\Delta t}{2}} + \Delta t a_i^t$ \;
	$x_i^{t+\Delta t} = x_i^t + \Delta t v_i^{t+\frac{\Delta t}{2}}$ \;	
	$a_i^{t + \Delta t} = a_i^{t + \Delta t} (x_i^{t + \Delta t}, m_i)$ from equation \ref{math:acceleration} \;
\end{algorithm}
